Constraint Programming - Inside Gecode

### 2014-05-03 paper.tex
branch-and-bound

	\subsubsection{Branch-and-Bound Search}

>>>>

	\subsubsection{Branch-and-Bound Search}
	Branch-and-bound refers actually to two parts, a Branch-and-reduce search and bounding. Branch-and-reduce itself is the continous constraint propagation to reduce the variable domains combined with branching when there is no further reduction by constraint propagation possible. A simple heuristic for branching would be to split the biggest domain into two equal sized intervals.
	Bounding is then the step which transforms the Branch-and-reduce search into an optimization. To be able to do this an objective function is necessary, which can be inverted.
